Board Game Recommendation

### 2015-04-08 paper.Rnw
've contraction

For data, we turn to \url{boardgamegeek.com}, a website that holds information, ratings, and reviews for over 75,000 games. Users can create an account and then rate games they've played as well as keep an inventory of games they own. All of this information is accessible and scrape-able, and is the data that drives our analysis.

@@

After we fit the general effects, we wish to model the remaining residuals, ideally in some way that gives us informative numeric summaries about the individual users in the process. In addition, we'd also like to compare a users ratings to other users, and hopefully use the behavior of similar users to predict new ratings for someone. A tempting first step is to, for a particular game, find other people who have rated that game who have rated games that you've rated. Then, you could find people who rated games similarly to you, and use their ratings of the new game as an estimate. This often does not work, as sometimes the number of people who have rated the same games as you can be relatively low, if not 0 (show a graph for this part).

To get around the problem of low crossover in game ratings, we turn to the characteristics of the games themselves. This kills two birds with one stone. We  create, for each user, a rating for each game mechanic and genre. Then, since there are so many mechanics and genres of game, a player only needs to rate a small, albeit diverse set of games before we can correlate that player's habits with other players, even if they've never played any of the same games! Then we can use those to filter rating results, as we   know what board game mechanics that a particular player  enjoy.

@@

\subsubsection{Back to Rating}
From what we've produced above in equations (2)-(9), of the estimated rating for user $u$ and game $i$ is given by:

@@

In an implementation of this, the application  begins by having the user enter the username they've registered on \url{boardgamegeek.com}. As seen in (~\ref{fig:blanksc}), there is an area to enter the users information in, and a button just below that, when clicked, begins the process.
\begin{center}
\begin{figure}\centering
\includegraphics[scale=0.4]{blank_login.png}
\caption{\label{fig:blanksc} A blank log in screen}
\end{figure}
\end{center}
Instead of logging the users ratings directly through the application, we  leverage the existing infrastructure of board game geek. After checking that its a valid username, the application  scours {\tt boardgamegeek} to see if the database's information is complete: that is, do we have this user's data in the player key? Have they rated games that are not   in our database? Have they re rated games that are in our database? Have they rated games that are not   in our database? If so, we also need to bring in other users ratings for any games that we may not have had in our database (as a single rating for a game is not   very useful and  greatly skews the results for that game). After this initial step and database update, we can see if they already have saved predicted ratings in the system, and if not, we   proceed to fit the model.

>>>>

For data, we turn to \url{boardgamegeek.com}, a website that holds information, ratings, and reviews for over 75,000 games. Users can create an account and then rate games they have  played as well as keep an inventory of games they own. All of this information is accessible and scrape-able, and is the data that drives our analysis.

@@

After we fit the general effects, we wish to model the remaining residuals, ideally in some way that gives us informative numeric summaries about the individual users in the process. In addition, we'd also like to compare a users ratings to other users, and hopefully use the behavior of similar users to predict new ratings for someone. A tempting first step is to, for a particular game, find other people who have rated that game who have rated games that you have  rated. Then, you could find people who rated games similarly to you, and use their ratings of the new game as an estimate. This often does not work, as sometimes the number of people who have rated the same games as you can be relatively low, if not 0 (show a graph for this part).

To get around the problem of low crossover in game ratings, we turn to the characteristics of the games themselves. This kills two birds with one stone. We  create, for each user, a rating for each game mechanic and genre. Then, since there are so many mechanics and genres of game, a player only needs to rate a small, albeit diverse set of games before we can correlate that player's habits with other players, even if they have  never played any of the same games! Then we can use those to filter rating results, as we   know what board game mechanics that a particular player  enjoy.

@@

\subsubsection{Back to Rating}
From what we have  produced above in equations (2)-(9), of the estimated rating for user $u$ and game $i$ is given by:

@@

In an implementation of this, the application  begins by having the user enter the username they have  registered on \url{boardgamegeek.com}. As seen in (~\ref{fig:blanksc}), there is an area to enter the users information in, and a button just below that, when clicked, begins the process.
\begin{center}
\begin{figure}\centering
\includegraphics[scale=0.4]{blank_login.png}
\caption{\label{fig:blanksc} A blank log in screen}
\end{figure}
\end{center}
Instead of logging the users ratings directly through the application, we  leverage the existing infrastructure of board game geek. After checking that its a valid username, the application  scours {\tt boardgamegeek} to see if the database's information is complete: that is, do we have this user's data in the player key? Have they rated games that are not   in our database? Have they re rated games that are in our database? Have they rated games that are not   in our database? If so, we also need to bring in other users ratings for any games that we may not have had in our database (as a single rating for a game is not   very useful and  greatly skews the results for that game). After this initial step and database update, we can see if they already have saved predicted ratings in the system, and if not, we   proceed to fit the model.
